---
title: "Sentiment Analysis for Amazon Phone Reviews"
author: "Andrew Zhang"
date: "12/16/2018"
output: ioslides_presentation
---
## Background

* Amazon is a huge marketplace for items
    + School supplies, food, electronics
* Customers leave reviews for items
    + Ratings, comments
* Ratings system for each item
    + 1 to 5 rating

## Goals
* Sentiment Analysis
* Understand the differences between positive and negative sentiments
    + Unique characteristics of reviews?

```{r, include = FALSE}
amazon <- read.csv("Amazon_Unlocked_Mobile.csv")
```

```{r, include = FALSE}
library(knitr)
variable_names <- colnames(amazon)
descriptions <- c('Name of the Product',
'Company that created the product',
'Amount of money for the product',
'Rating a customer gives the product(Out of 5)',
'Written comments regarding the product',
'Number of votes a review gets')
var_table <- data.frame(variable_names, descriptions)
```

## Variables

```{r, echo = FALSE}
kable(var_table, caption = "Variables")
```

```{r, subset, include = FALSE}
library(caret)
library(dplyr)

amazon$Brand.Name <- tolower(as.character(amazon$Brand.Name))

amazon_counts <- amazon %>% 
  count(Product.Name, sort = TRUE)

amazon_counts2 <- amazon %>% 
  count(Brand.Name, sort = TRUE)

brand_counts <- amazon %>% 
  group_by(Product.Name) %>% 
  count(Product.Name, sort = TRUE) 

sub <- brand_counts[brand_counts$n > 800,]

amazon_sub <- amazon[amazon$Product.Name %in% sub$Product.Name, ]

amazon_sub <- amazon_sub %>% 
  group_by(Product.Name) %>% 
  mutate(id = row_number())

amazon_sub$Brand.Name[amazon_sub$Brand.Name == "samsung korea ltd"] <- "samsung"
```

```{r, include = FALSE}
library(tidyverse)
str(amazon_sub)

amazon_sub[amazon_sub$Brand.Name == "",] <- NA
colSums(is.na(amazon_sub))
amazon_sub <- na.omit(amazon_sub)

brand_counts <- amazon_sub %>% 
  group_by(Brand.Name) %>% 
  summarize(Count = length(Brand.Name))

length(unique(amazon_sub$Product.Name))
length(unique(amazon_sub$Brand.Name))

new <- c()
new <- data.frame(lapply(amazon_sub$Reviews, as.character), stringsAsFactors = FALSE)
trans_new <- t(new)
amazon_sub$Reviews <- trans_new[1:54198]

amazon_sub$Word_Count <- sapply(strsplit(amazon_sub$Reviews, " "), length)

amazon_explore <- amazon_sub %>% 
  group_by(Product.Name, Brand.Name) %>% 
  summarize(Price.Avg = mean(Price),
            Rating.Avg = mean(Rating),
            ReviewVotes.Avg = mean(Review.Votes),
            WordCount.Avg = mean(Word_Count))
```

```{r, include = FALSE}
install.packages("corrplot", repos='http://cran.us.r-project.org')
library(corrplot)

cor_sub <- amazon_explore %>% 
  select(Price.Avg, Rating.Avg, ReviewVotes.Avg, WordCount.Avg)
cor_sub$Product.Name <- NULL

amazon_cor <- cor(cor_sub)
```

## Data Cleaning/Exploration

* Look at the structure of the data
* Clean out missing data
* Aggregate data for exploration
* Positive and Negative sentiments
* Add word counts
* Filter data for biggest brands

## Correlation Plot

```{r, echo = FALSE, out.width = "75%", fig.align="center"}
corrplot(amazon_cor, method = "ellipse")
```

* Ratings/Price are positively correlated
* Word Counts/Review Votes are positive correlated
* Ratings/Review Votes are negatively correlated

```{r, exploratory plots, include = FALSE}
library(ggpubr)
library(magrittr)
ep1 <- ggplot(amazon_explore) +
  aes(ReviewVotes.Avg, Rating.Avg) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_minimal() +
  labs(title = "Review Votes vs. Ratings")

ep2 <- ggplot(amazon_explore) +
  aes(log(Price.Avg), Rating.Avg) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_minimal() +
  labs(title = "Price vs. Rating")

ep3 <- ggplot(amazon_explore) +
  aes(log(WordCount.Avg), Rating.Avg) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_minimal() +
  labs(title = "Word Counts vs. Rating")

ep4 <- ggplot(amazon_explore) +
  aes(log(Price.Avg), log(WordCount.Avg)) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_minimal() +
  labs(title = "Price vs. Word Count")
```

```{r, sentiment analysis, include = FALSE}
library(tidytext)
colnames(amazon_sub)[5] <- c("text")
review_words <- amazon_sub %>% unnest_tokens(output = word, input = text)

data("stop_words")
tidy_words <- review_words %>%
  anti_join(stop_words)
```

```{r, get positive/negative, include = FALSE}
afinn <- get_sentiments("afinn")
nrc <- get_sentiments("nrc")
bing <- get_sentiments("bing")

rw_bing <- tidy_words %>% 
  inner_join(bing)

rw_bingafinn <- rw_bing %>% 
  inner_join(afinn, by = "word")

## Explore number of positive words and negative words
rw_explore <- rw_bingafinn %>% 
  group_by(Product.Name, Brand.Name, sentiment) %>% 
  summarize(Price.Avg = mean(Price),
            Rating.Avg = mean(Rating),
            ReviewVotes.Avg = mean(Review.Votes),
            WordCount.Avg = mean(Word_Count), 
            Score.Avg = mean(score))
```

## Negative vs. Positive Distribution
```{r, plot sentiments, echo = FALSE, out.width = "75%", fig.align="center"}
ggplot(data = rw_explore) +
  aes(x = reorder(Product.Name, WordCount.Avg), color = sentiment, weight = WordCount.Avg) +
  geom_bar(fill = '#0c4c8a') +
  labs(title = 'Sentiment Counts',
    x = 'Product Name',
    y = 'Number of Words') +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  coord_flip()
```

* More words for negative reviews
* Potentially more descriptive

```{r, preprocess, include = FALSE}
str(rw_bingafinn)

rw_bingafinn$Brand.Name <- factor(rw_bingafinn$Brand.Name)
rw_bingafinn$Price <- log(rw_bingafinn$Price)
rw_bingafinn$Review.Votes[rw_bingafinn$Review.Votes == 0] <- 1
rw_bingafinn$Review.Votes <- log(rw_bingafinn$Review.Votes)
rw_bingafinn$Word_Count <- log(rw_bingafinn$Word_Count)

colSums(is.na(rw_bingafinn))
rw_bingafinn <- na.omit(rw_bingafinn)
```

# Pattern Analysis

## Ratings vs. Price
```{r, EDA, echo = FALSE, warning=FALSE, out.width = "75%", fig.align="center"}
#esquisse::esquisser(rw_bingafinn)
library(ggplot2)

ggplot(data = rw_bingafinn) +
  aes(x = Rating, y = Price, color = sentiment) +
  geom_point() +
  theme_minimal() +
  facet_wrap(vars(Brand.Name)) +
  labs(title = "Ratings vs. Price")
```

* Negative sentiment = lower rating
* Positive sentiment = higher rating

## Word Count vs. Review Votes
```{r, echo = FALSE, out.width = "75%", fig.align="center"}
ggplot(data = rw_bingafinn) +
  aes(x = Word_Count, y = Review.Votes, color = sentiment) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_minimal() +
  facet_wrap(vars(Brand.Name)) + 
  labs(title = "Word Count vs. Review Votes")
```

* Upward trend for both positive and negative sentiments
* More words can lead to a higher number of review votes

## Ratings vs. Review Votes
```{r, echo = FALSE, out.width = "75%", fig.align="center"}
ggplot(data = rw_bingafinn) +
  aes(x = Rating, y = Review.Votes, color = Brand.Name) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_minimal() +
  labs(title = "Ratings vs. Review.Votes")
```

* Increase in ratings means a decrease in review votes
* Inverse relationship
* Reflective of negative correlation

```{r, include = FALSE}
ggplot(data = rw_bingafinn) +
  aes(x = sentiment) +
  geom_bar(fill = '#0c4c8a') +
  theme_minimal() + 
  labs(title = "Positive vs. Negative Distribution")
```

## Distribution of Word Counts
```{r, echo = FALSE, out.width = "80%", fig.align="center"}
ggplot(data = rw_bingafinn) +
  aes(x = Word_Count, color = sentiment) +
  geom_histogram(bins = 30, fill = '#0c4c8a') +
  labs(title = 'Distribution of Word Counts') +
  theme_minimal() +
  facet_wrap(vars(Brand.Name))
```

* Significantly more words for negative sentiment than positive words

## Review Meanings
```{r, plots, echo = FALSE, out.width = "75%", fig.align="center"}
words_brand <- tidy_words %>% 
  group_by(Brand.Name) %>% 
  count(word, sort = TRUE)

words_count <- tidy_words %>% 
  group_by(word) %>% 
  count(word, sort = TRUE)

words_count %>%
  filter(n > 2900) %>% 
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_col(fill = '#0c4c8a') +
  xlab(NULL) +
  labs(title = "Most Popular Words") +
  coord_flip()
```

* *phone* is the most popular word in all reviews
* Words are mainly feature related
* iphone and Samsungs are incredibly popular

```{r, bing word count, include = FALSE}
bing_word_counts <- tidy_words %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts
```

## Review Meanings cont.
```{r, echo = FALSE, out.width = "70%", fig.align="center"}
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(20) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = reorder(word, n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
```

* Positive words are subjective
* Negative words seem to be more feature based and technical
* Negative words get more votes and words

```{r, include = FALSE}
install.packages("benford.analysis", repos='http://cran.us.r-project.org')
library(benford.analysis)
library(tidyverse)

## Product Counts
revcounts <- amazon_counts$n

revcounts_b <- benford(revcounts)

chisq(revcounts_b)

## Brand Counts
revcounts2 <- amazon_counts2$n

revcounts_b2 <- benford(revcounts2)

chisq(revcounts_b2)
```

# Benford Analysis
## Benford Analysis for Product Names
```{r, echo = FALSE, fig.align="center"}
plot(revcounts_b)
```

## Benford Analysis for Brand Names
```{r, echo = FALSE, fig.align="center"}
plot(revcounts_b2)
```

## Conclusion
* Negative reviews had more words than positive reviews
* The more words in a review, the more review votes it had
    + Sincere reviews have more words
* Negative reviews have more words
    + More words = more review votes
    + Negative reviews have more review votes
* Product Names and Brand Name don't follow Benford
    + Fake reviews/"meme" reviews

## Future Works
* In depth sentiment analysis for brands
    + Apple, Samsung
* Creating models based on ratings, prices, number of words, etc
